Temporality is Important for Networks of Hospital Patient Transfers

### 2025-04-02 reports/report.qmd
small push on bibs refs

---
title: "Temporality is Important for Networks of Hospital Patient Transfers"
authors:
    - name: David Wu
    - name: Michael Lydeamore
    - name: Andrew Stewardson
    - name: Tjibbe Donker
    - name: Nic Geard
    - name: "******"
date: last-modified
format:
    html: default
    pdf:
        include-in-header:
            - text: |
                \usepackage{mathtools}
        papersize: a4
bibliography: refs.bib
csl: plos.csl
filters:
    - diagram
jupyter: python3
execute:
    echo: false
    warning: false
    error: false
---

@@

Existing studies treating hospital systems as networks

A network or graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ is made up of nodes or vertices $\mathcal{V} = \{v_1, v_2, \dots\}$ and edges $\mathcal{E} = \{e_{ij} \coloneqq (v_i, v_j)\}$ that join those nodes. Each edge $e_{ij}$ can be assigned attributes, including an edge weight $w_{ij}$.
For our application, this edge weight will typically represent the number of observed movements in a given time period. Thus the network can encode a representation of the movement between hospitals over a given time period.

We can use the network to construct a Markov chain, where the expected rate of movement is governed by the observed movement in the data. For some edge $e_{ij}$ with a number of observed movements $w_{ij}$ over some time period $\tau$, the rate of movement along that edge $\lambda_{ij} = w_{ij} / \tau$, such that the time between movement events along that edge are exponentially distributed $\text{Exp}(\lambda_{ij})$.

[Stuff about previous implementations of this idea]

@@

We can then say that 
:::

>>>>

---
title: "Temporality is Important for Networks of Hospital Patient Transfers"
authors:
    - name: David Wu
    - name: Michael Lydeamore
    - name: Andrew Stewardson
    - name: Tjibbe Donker
    - name: Nic Geard
    - name: "******"
date: last-modified
format:
    html: default
    pdf:
        include-in-header:
            - text: |
                \usepackage{mathtools}
        papersize: a4
bibliography: refs.bib
csl: plos.csl
filters:
    - tikz 
jupyter: python3
execute:
    echo: false
    warning: false
    error: false
    eval: false
callout-appearance: simple
---

@@

There has been some existing work that analyse hospital systems using the framework of network analysis. 
They define a network consisting of hospitals as nodes, connected by edges that have weights representative of the amount of patient movement between those hospitals.
Using these networks, hospitals and links that are important to movement around the hospital system by analysing measures of centrality and clustering.
<!-- Thus the network can encode a representation of the movement between hospitals over a given time period. -->

A weighted, directed network can be used to construct a Markov chain that in turn can be analysed or simulated to understand

For some edge $e_{ij}$ with a number of observed movements $w_{ij}$ over some time period $\tau$, the rate of movement along that edge $\lambda_{ij} = w_{ij} / \tau$, such that the time between movement events along that edge are exponentially distributed $\text{Exp}(\lambda_{ij})$.

:::{.callout-note} 
[Stuff about previous implementations of this idea] 
:::

@@

We can then say that
